probKanren: A Simple Probabilistic extension for miniKanren

### 2021-07-25 paper/main.tex
Add title
added Will's affiliation

%%
%% The "title" command
\title{A better way to format your document for CEUR-WS}

@@

\author[2]{William E. Byrd}[%
%orcid=0000-0001-7116-9338,
email=webyrd@uab.edu,
url=http://webyrd.net/,
]
\address[2]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}

>>>>

%%
%% The "title" command
\title{probKanren: A Simple Probabilistic extension for miniKanren}

@@

\author[2]{William E. Byrd}[%
%orcid=0000-0001-7116-9338,
email=webyrd@uab.edu,
url=http://webyrd.net/,
]
\address[2]{Hugh Kaul Precision Medicine Institute, University of Alabama at Birmingham, 705 20th Street S., Birmingham, AL 35233, United States of America}
